Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-26 document/ms.tex
bibitem
cite Dong

This study is novel in a number of ways.
We create probabilistic information about the full exoplanet population
\emph{not} by weighting the detected objects by the inverse detection
efficiency (CITE PETIGURA), but rather by forward modeling the observed
distribution subject to the detection efficienty.
Re-weighting the data by inverse selection probability---a method called
V-max in the quasar and galaxy luminosity function contexts---is not wrong,
but it produces a higher-variance estimate of the population than a justified
likelihood approach.
One simple intuition along these lines is that the inverse probability weights
can be large in dynamic range, so the effective number of samples, after
weighting, can be much smaller than the actual number of samples.
Another is that it tends to upweight most strongly the most marginal
detections in the data sample, since these tend to be the samples that lie in
the region of lowest completeness.  In this work, we build a justified
likelihood of the observed data, taking into account the completeness function
or detection efficiency.
Our likelihood function is a variable-rate Poisson likelihood; it makes the
fundamental assumption that the data points are independently drawn from the
model, but is agnostic about all other properties of the data or distribution
functions.
Indeed, the assumptions behind this study are weaker than those of any
previous study of the Earth-analog population (CITE PETIGURA, DONG).

@@

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Petigura \etal(2013)]{petigura}
Petigura, E.~A., Howard, A.~W., \& Marcy, G.~W.\ 2013,
Proceedings of the National Academy of Science, 110, 19273

\end{thebibliography}

>>>>

This study is novel in a number of ways.
We create probabilistic information about the full exoplanet population
\emph{not} by weighting the detected objects by the inverse detection
efficiency (CITE PETIGURA), but rather by forward modeling the observed
distribution subject to the detection efficienty.
Re-weighting the data by inverse selection probability---a method called
V-max in the quasar and galaxy luminosity function contexts---is not wrong,
but it produces a higher-variance estimate of the population than a justified
likelihood approach.
One simple intuition along these lines is that the inverse probability weights
can be large in dynamic range, so the effective number of samples, after
weighting, can be much smaller than the actual number of samples.
Another is that it tends to upweight most strongly the most marginal
detections in the data sample, since these tend to be the samples that lie in
the region of lowest completeness.  In this work, we build a justified
likelihood of the observed data, taking into account the completeness function
or detection efficiency.
Our likelihood function is a variable-rate Poisson likelihood; it makes the
fundamental assumption that the data points are independently drawn from the
model, but is agnostic about all other properties of the data or distribution
functions.
Indeed, the assumptions behind this study are weaker than those of any
previous study of the radius and period distribution of the Earth-analog
population (\citealt{dong, petigura}).

@@

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright
\bibitem[Dong \& Zhu(2013)]{dong}
Dong, S., \& Zhu, Z.\ 2013, \apj, 778, 53 
\bibitem[Petigura \etal(2013)]{petigura}
Petigura, E.~A., Howard, A.~W., \& Marcy, G.~W.\ 2013,
Proceedings of the National Academy of Science, 110, 19273
\end{thebibliography}
